Emotional framing and the effectiveness of corrective information^[I thank Thomas Bräuninger, Sebastian Juhl, the GIP team, and participants of the CDSS workshop in political science for excellent comments and helpful suggestions on this study. This work was supported by the German Research Foundati

### 2021-09-10 paper.Rmd
references from citavi or google drive

bibliography: references.bib
csl: american-journal-of-political-science.csl
output:
  bookdown::pdf_document2:
    toc: no
    keep_tex: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin=1in
always_allow_html: yes

>>>>

bibliography: references.bib # to be downloaded from citavi or google drive
csl: american-journal-of-political-science.csl # https://github.com/citation-style-language/styles
output:
  bookdown::pdf_document2:
    toc: no
    keep_tex: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin=1in
always_allow_html: yes
